\documentclass[8pt, a4paper]{article}
	\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=1.5cm]{geometry}

    \title{\textbf{Geometric Phase in Quantum Theory: 
    \\ It's relevence from Schrödinger to Schwarzschild}}
    
    
    \author{}
    \date{I don't know when.07.2021}
    

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{chngcntr}
\usepackage{braket}
\usepackage{esint}
\usepackage{graphicx}




\begin{document}
\begin{thebibliography}{}

\bibitem[1]{schuller} \href{https://mathswithphysics.blogspot.com/2016/07/frederic-schullers-lectures-on-quantum.html}{Lectures on Quantum Theory by Frederic P. Schuller Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU)}
 
 \bibitem[2]{adiabaticberry} \href{https://ethz.ch/content/dam/ethz/special-interest/phys/theoretical-physics/itp-dam/documents/gaberdiel/proseminar_fs2018/05_Stengele.pdf}{Sebastian Stengele - Berry's Phase - Proseminar - Algebra, Topology, and Group Theory in Physics 2018}
 
 \bibitem[3]{berrypaper}\href{https://www.jstor.org/stable/2397741}{Quantal Phase Factors Accompanying Adiabatic Changes: 
M. V. Berry Proceedings of the Royal Society of London. Series A, Mathematical and Physical Sciences
Vol. 392, No. 1802 (Mar. 8, 1984), pp. 45-57 (13 pages)
Published By: Royal Society}

 \bibitem[4]{ab}\href{}{Significance of Electromagnetic Potentials in the Quantum Theory Y. Aharonov and D. Bohm}
 
 
 \bibitem[5]{geop}\href{}{The Geometric Phase in Quantum Systems  Bohm, A., Mostafazadeh, A., Koizumi, H., Niu, Q., Zwanziger, J}
  
  \bibitem[6]{pathAharonov}\href{}{Feynman path-integral approach to the Aharonov-Bohm effect
Christopher C. Gerry and Vijay A. Singh}

	\bibitem[7]{goodone} \href{https://physik.uni-graz.at/~uxh/diploma/orasch14.pdf}{The Aharonov-Bohm-Effect: Oliver Orasch: Karl-Franzens-Universität Graz}
	
	\bibitem[8]{simon} \href{}{Holonomy, the Quantum Adiabatic Theorem, and Berry's Phase: B. Simon
Phys. Rev. Lett. 51, 2167 – Published 12 December 1983}

\bibitem[9]{geomanatomy} \href{https://www.youtube.com/playlist?list=PLPH7f_7ZlzxTi6kS4vCmv4ZKm9u8g5yic}{lectures on Geometrical Anatomy of Theoretical Physics: Frederic Schuller }

\bibitem[10]{doeslie} \href{https://math.uchicago.edu/~may/REU2016/REUPapers/Mandel.pdf}{What does the lie algebra know about the lie group: Holy Mandel}
  
  \bibitem[11]{aharanovanandan}\href{}{Phase change during a cyclic quantum evolution
Y. Aharonov and J. Anandan
Phys. Rev. Lett. 58, 1593}
  
 
\end{thebibliography}

\end{document}\